---
title: "batch-calculate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{batch-calculate}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(agena.ai)
```

Setting the working directory to where we have the Models folder if needed

```{r}
#setwd("/Users/user/repos/api-r")
```

Importing an existing model from a .cmpx file

```{r}
model <- from_cmpx("CarCosts.cmpx")
network <- model$networks[[1]]
```

Creating an empty csv file template with all the networks and nodes in the model

```{r}
create_csv_template(model)
```

The dataset csv is manually prepared and filled in outside the R environment
In this example, it now includes five scenarios with different observations, and only the columns about the observed variables are kept

```{r}
inputData <- "CarCosts_DataSet_Modified.csv"
```

Creating batch cases, this function creates a new .json model file in the working directory with dataSets representing all the rows in the input data

```{r}
create_batch_cases(model, inputData)
```

It is possible to import the new model file back to R to work with it

```{r}
model_with_cases <- from_cmpx("Car Costs_0 Model_Batch_Cases.json")
```

Now model_with_cases is an R model object containing both the dataSets already existing in the model and a new dataSet for each row in the input data and it is ready to be used for calculation purposes

Running the local API batch calculate function to update the model object with all the results

```{r}
local_api_batch_calculate(model_with_cases)
```
