---
title: "calculate-cloud"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{calculate-cloud}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(agena.ai)
```

Setting the working directory to where we have the Models folder if needed

```{r}
#setwd("/Users/user/repos/api-r")
```

Importing an existing model from a .cmpx file

```{r}
model <- from_cmpx("CarCosts.cmpx")
```

Defining the dataSet of interest ("mercedes"), and finding the relevant dataSet object in the model

```{r}
dsId <- "mercedes"
dsIndex <- which(sapply(model$dataSets, function(sds) sds$id %in% dsId))
dataSet <- model$dataSets[[dsIndex]]
```

Assigning certain nodes in the network so that it is easier to manipulate them (such as entering new observation)

```{r}
network <- model$networks[[1]]

nodeCarType <- network$nodes[[which(sapply(network$nodes, function(item) item$id %in% "car_type"))]]
nodeMilesPerYear <- network$nodes[[which(sapply(network$nodes, function(item) item$id %in% "Miles_per_year"))]]
nodeReliability <- network$nodes[[which(sapply(network$nodes, function(item) item$id %in% "Reliability"))]]
nodeTotalAnnualCost <- network$nodes[[which(sapply(network$nodes, function(item) item$id %in% "total_cost"))]]
```

Entering new observations to the selected nodes

```{r}
model$enter_observation(dsId, node=nodeCarType$id, network=network$id, value="Small")
model$enter_observation(dsId, node=nodeMilesPerYear$id, network=network$id, value=1000)
model$enter_observation(dsId, node=nodeReliability$id, network=network$id, value="Low")
```

Login to the agena.ai cloud servers and calculating the model (with correct credentials)

```{r}
credentials <- login("test@example.com", "1234567890")
calculate(model, credentials, dataSet$id)
```

Accessing and displaying information which now is included in the model object

```{r}
resIndex <- which(sapply(model$dataSets[[dsIndex]]$results, function(res) res$node %in% "total_cost"))
model$dataSets[[dsIndex]]$results[[resIndex]]$node
model$dataSets[[dsIndex]]$results[[resIndex]]$summaryStatistics$mean
```
