---
title: "sensitivity-cloud"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sensitivity-cloud}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(agena.ai)
```

Setting the working directory to where we have the Models folder if needed

```{r}
#setwd("/Users/user/repos/api-r")
```

Importing an existing model from a .cmpx file

```{r}
model <- from_cmpx("CarCosts.cmpx")
network <- model$networks[[1]]
```


Creating a new dataSet in the model for sensitivity analysis

```{r}
model$create_dataSet(id = "sa")
```

Creating a sensitivity analysis config object which uses all nodes for sensitivity analysis on the node total_cost, to calculate mean and variance results

```{r}
sa_config <- create_sensitivity_config(
  target="total_cost",
  sensitivity_nodes="*",
  dataset="sa",
  report_settings = list(summaryStats = c("mean", "variance"))
)
```

Login to the agena.ai cloud servers and running the sensitivity analysis

```{r}
credentials <- login("test@example.com", "1234567890")

sensitivity_analysis(model, credentials, sa_config)
```
